Transparency of COVID-19-related research in medical journals

### 2022-04-15 manuscript_covid_transparency.qmd
minor edit to methods

To do so, we used a validated and automated tool developed by Serghiou et al. [@serghiou2021] suitable to identify these five transparent practices from articles in XML format from the EPMC database. Regarding data sharing, code sharing and protocol registration the tool identifies whether the article had actually adhered to practice (for instance "data available on request" are not counted as sharing data), whereas COI and funding disclosure merely detect whether articles included the disclosure or not (regardless of its content) [@serghiou2021].

>>>>

To do so, we used a validated and automated tool developed by Serghiou et al. [@serghiou2021] suitable to identify these five transparent practices from articles in XML format from the EPMC database. Regarding data sharing, code sharing and protocol registration the tool identifies whether the article had actually adhered to practice (for instance "data available on request" are not counted as sharing data), whereas COI and funding disclosure merely detect whether articles include the disclosure or not (regardless of its specific content) [@serghiou2021].
